---
title: "fake_lab 1"
author: "Pete"
format: html
---

## Introduction

This is the first iteration of fake lab. Our goal here is to simulate four simple scenarios that can feed a basic Bayesian intercomparison model. 

The fake lab will have five instruments, three operators and will be churning out reference measurement. 

The refernce material has a true value of 50 u (u stands for some unit). Instruments measure this with a normal error of N(0,5). Operators add a further N(0,5) worth of noise.

In scenario 1 everything works perfect.
In scenario 2 one of the instruments introduces an offset of N(2, 6) instead of the expected N(0, 5).
In scenario 3 the machines are working well, but one of the operators is clumsy - and adds N(0,8) uncertainty rather than N(0,5).
In scenario 4 I include both the faulty machine and the clumsy operator. 

Each scenario consists of 1000 measurements randomly assigned between the operators and the instruments. 



## Set up
```{r}
library(tidyverse)
```


```{r}
instruments <- c("instrument_1", "instrument_2", "instrument_3", "instrument_4", 
                 "instrument_5")
operators <- c("operator_1", "operator_2", "operator_3")
```


## Scenario 1

The no error scenario
```{r}
scenario_1 <- data.frame(
  measurement_id = seq(1, 1000, 1),
  instrument = sample(instruments, 1000, TRUE),
  operator = sample(operators, 1000, TRUE),
  ref_value = 50
  ) |>
  mutate(
    instrument_offset = 0,
    instrument_error = 5,
    operator_offset = 0,
    operator_error = 5
  ) |>
mutate(
  measurement = pmap(list(1, 
                      mean = 50 + instrument_offset + operator_offset,
                      sd = sqrt(instrument_error ^ 2 + operator_error ^ 2)),
                     rnorm)
)
```


